---
title: "Assessing Student Understanding"
author: "STAT 375 UC Berkeley"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: solarized-light
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      fig.align = "center",
                      fig.retina = 3,
                      warning = FALSE)

library(tidyverse)
library(emo)
library(lorem)
library(xaringanthemer)
library(countdown)
source("https://raw.githubusercontent.com/andrewpbray/stat-375-website/master/xaringan-theme.R")
```

---
## Agenda

1. Reflections from teaching
2. Types of Assessments
2. Purpose of Grading
3. What to do about grades
 - Eric Mazur
 - Debate
4. Break
5. Writing good questions
  - Bloom's Taxonomy
  - Question Workshop


---
class: middle, center, inverse

# Reflections from teaching

---
## Reflections from teaching

.task[
In your groups, take turns sharing what active learning exercise you tried this last week in class and how it went. Otherwise, share:

1. One thing that went well
2. One thing that went poorly
3. One thing you learned
]

```{r echo = FALSE}
countdown(minutes = 10, bottom = 0)
```

---
class: middle, center, inverse

# Assessments and Grades

---

## Three types of Assessments
--

1. **Diagnostic**
--

2. **Formative**
--

3. **Summative**

---

<iframe width="1120" height="630" src="https://www.youtube.com/embed/JI-YgK-l4Sg" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---
## What do assessments look like?
--

.pull-left[
- Exams
- Quizzes
- Essays
- Presentations
]

--

.pull-left[
- Labs
- Projects
- Quick writes
- In class questions
]

--

- Practice problems?

--

_Assessments_ can be anything the instructor asks of the student to assess their level of understanding; opportunities provided to students to demonstrate their own understanding.


???
Discussion: Items meant purely for practice, like some homework, might not be considered an assessment and might not be graded.

---
## What are grades?
--

> ...the practically universal use in all
educational institutions of a system of marks, whether
numbers or letters, to indicate scholastic attainment of
the pupils or students in these institutions...
- I. E. Finkelstein

---
class: middle, center

# Disclaimer
--

.adage[The system of grading in your class is more or less out of your hands at the moment.]


---
## Purposes of Grading
--

1. Grades as Feedback on Performance
--

2. Grades as a Motivator of Student Effort
--

3. Grades as a Tool for Comparing Students
--

4. Grades as an Objective Evaluation of Student
Knowledge


---
## 1. Grades as Feedback on Performance

> What kinds of feedback are there? Does it work?

--

- Feedback can be descriptive (here's what you need to do) or evaluative (here's where you're at).

--

- "the grade trumps the comment"

--

- Unclear if comments are read and understood.

---
## 2. Grades as Motivator of Student Effort

> Does it work? For whom?

--

- Grades generally inhibit motivation (except in high achievers).

--

- Extrinsic motivation supplants intrinsic motivation.

--

???
Study to mention: Regular volunteers (e.g. Kiwanas) provided payment for volunteerism see a decline in hours volunteered over a control, non-compensated group.


---
## 3. Grades as Tool for Comparing Students

> Does it work? What are the side-effects?

--

- Competition between students inhibits overall learning.

--

- Curved grades no longer reflect mastery.


---
## 4. Grades as an Objective Evaluation of Student Knowledge

> When does it work? When doesn't it?

--

- Objective (MC questions) grading as fair but artificial.

--

- Subjective grading of writing very inconsistent between and within instructors.

--

- Rubrics help.


---
## PI-style Question

Recall the structure of a PI Question.

1. Solo think and poll
2. Discuss with table. Move if no disagreement.
3. Repoll
4. Share as class

--

Prepare to poll: 

---

.pull-left[
### Model A

Students are given written feedback on assignments instead of grades. At the end of the course, they get a written summary.

### Model C

Students get feedback on assignments but the grades are hidden from them until the completion of the course. At 8 weeks, they're notified whether or not they're on track to pass the course.
]

.pull-right[
### Model B

Students are only given feedback, not grades, while taking a course. They have the option, though, of registering for a separate examination by an external evaluator.

### Model D

Students are given a grade on every assignment and the rubric for evaluation is made completely transparent. They know their progress at all times.
]

```{r echo = FALSE}
countdown(minutes = 0, 
          seconds = 30, 
          bottom = 0, 
          font_size = "1em",
          warn_when = 10)
```

---

.pull-left[
### Model A

Students are given written feedback on assignments instead of grades. At the end of the course, they get a written summary.

### Model C

Students get feedback on assignments but the grades are hidden from them until the completion of the course. At 8 weeks, they're notified whether or not they're on track to pass the course.
]

.pull-right[
### Model B

Students are only given feedback, not grades, while taking a course. They have the option, though, of registering for a separate examination by an external evaluator.

### Model D

Students are given a grade on every assignment and the rubric for evaluation is made completely transparent. They know their progress at all times.
]

```{r echo = FALSE}
countdown(minutes = 8, 
          bottom = 0, 
          font_size = "1em",
          warn_when = 10)
```

---

<center>
<iframe src="https://embed.polleverywhere.com/multiple_choice_polls/OMwwmmtRuyDcQfbdBG0Yb?controls=none&short_poll=true" width="800px" height="600px"></iframe>
</center>

---

<center>
<iframe src="https://embed.polleverywhere.com/multiple_choice_polls/8cPfH44JDibVtbX8CF66E?controls=none&short_poll=true" width="800px" height="600px"></iframe>
</center>

---

## Break

```{r echo = FALSE}
countdown(minutes = 5, 
          bottom = 0, 
          font_size = "1em",
          warn_when = 10)
```

---
class: center, middle, inverse

# Writing Good Questions

---
## Blooms Taxonomy

---
## Example 1

Which level of the hierarchy is tested by the following question?

---
## Example 2

Which level of the hierarchy is tested by the following question?

---
## Example 3

Which level of the hierarchy is tested by the following question?

---
## Question workshop part I

With the people at your table, take turns sharing your question and addressing

1. The concept(s) that it assesses.
2. The form of inquiry it assesses based on Bloom's.
3. What you like / dislike about the question.
4. Where/how a student could misinterpret the question.
5. How difficult it will be to grade.

```{r echo = FALSE}
countdown(minutes = 10, 
          font_size = "3em",
          warn_when = 10)
```

---
## Question workshop part II

Select one of your groups question as a candidate for revisions.

1. Upload the question to the google doc.
2. Rewrite the question into a second version that is **more** challenging.
3. Rewrite the question into a third version that is **less** challenging.

Link to the google doc: `shorturl.at/btvF9`

```{r echo = FALSE, fig.height = 3.5}
plot(qrcode::qr_code("shorturl.at/btvF9"))
```


```{r echo = FALSE}
countdown(minutes = 6, 
          font_size = "3em",
          warn_when = 10)
```