---
title: "Assessing Student Understanding"
author: "STAT 375 UC Berkeley"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: solarized-light
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      fig.align = "center",
                      fig.retina = 3,
                      warning = FALSE)

library(tidyverse)
library(emo)
library(lorem)
library(xaringanthemer)
library(countdown)
source("https://raw.githubusercontent.com/andrewpbray/stat-375-website/master/xaringan-theme.R")
```

---
## Agenda

1. Reflections from teaching
2. Types of Assessments
2. Purpose of Grading
3. What to do about grades
 - Eric Mazur
 - Debate
4. Break
5. Writing good questions
  - Bloom's Taxonomy
  - Question Workshop


---
class: middle, center, inverse

# Reflections from teaching

---
## Reflections from teaching

.task[
In your groups, take turns sharing what active learning exercise you tried this last week in class and how it went. Otherwise, share:

1. One thing that went well
2. One thing that went poorly
3. One thing you learned
]

```{r echo = FALSE}
countdown(minutes = 10, bottom = 0)
```

---
class: middle, center, inverse

# Assessments and Grades

---

## Three types of Assessments
--

1. **Diagnostic**
--

2. **Formative**
--

3. **Summative**

---

<iframe width="1120" height="630" src="https://www.youtube.com/embed/JI-YgK-l4Sg" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---
## What do assessments look like?
--

.pull-left[
- Exams
- Quizzes
- Essays
- Presentations
]

--

.pull-left[
- Labs
- Projects
- Quick writes
- In class questions
]

--

- Practice problems?

--

_Assessments_ can be anything the instructor asks of the student to assess their level of understanding; opportunities provided to students to demonstrate their own understanding.


???
Assessments can be anything the instructor asks of the student to assess their level of understanding; opportunities provided to students to demonstrate their own understanding. Items meant purely for practice, like some homework, might not be considered an assessment and might not be graded.

---
## What are grades?
--

> ...the practically universal use in all
educational institutions of a system of marks, whether
numbers or letters, to indicate scholastic attainment of
the pupils or students in these institutions...
- I. E. Finkelstein

---
class: middle, center

# Disclaimer
--

.adage[The system of grading in your class is more or less out of your hands at the moment.]


---
## Purposes of Grading
--

1. Grades as Feedback on Performance
--

2. Grades as a Motivator of Student Effort
--

3. Grades as a Tool for Comparing Students
--

4. Grades as an Objective Evaluation of Student
Knowledge


---
## 1. Grades as Feedback on Performance

> What kinds of feedback are there? Does it work?

--

- Feedback can be descriptive (here's what you need to do) or evaluative (here's where you're at).

--

- "the grade trumps the comment"

--

- Unclear if comments are read and understood.

---
## 2. Grades as Motivator of Student Effort

> Does it work? For whom?

--

- 


---
## 3. Grades as Tool for Comparing Students

> Does it work? What are the side-effects?

--

- Competition between students inhibits overall learning.

--

- Curved grades no longer reflect mastery.


---
## 4. Grades as an Objective Evaluation of Student Knowledge

> When does it work? When doesn't it?

--

- Objective (MC questions) grading as fair but artificial.

--

- Subjective grading of writing very inconsistent between and within instructors.

---

- Rubrics help.


---
## PI-style Question

Recall the structure of a PI Question.

1. Solo think and poll
2. Discuss with table. Move if no disagreement.
3. Repoll
4. Share as class

--

Prepare to poll: 

---

.pull-left[
### Model A

Students are given written feedback on assignments instead of grades. At the end of the course, they get a written summary.

### Model C

Students get feedback on assignments but the grades are hidden from them until the completion of the course. At 8 weeks, they're notified whether or not they're on track to pass the course.
]

.pull-right[
### Model B

Students are only given feedback, not grades, while taking a course. They have the option, though, of registering for a separate examination by an external evaluator.

### Model D

Students are given a grade on every assignment and the rubric for evaluation is made completely transparent. They know their progress at all times.
]

```{r echo = FALSE}
countdown(minutes = 0, 
          seconds = 30, 
          bottom = 0, 
          font_size = "1em",
          warn_when = 10)
```

---

.pull-left[
### Model A

Students are given written feedback on assignments instead of grades. At the end of the course, they get a written summary.

### Model C

Students get feedback on assignments but the grades are hidden from them until the completion of the course. At 8 weeks, they're notified whether or not they're on track to pass the course.
]

.pull-right[
### Model B

Students are only given feedback, not grades, while taking a course. They have the option, though, of registering for a separate examination by an external evaluator.

### Model D

Students are given a grade on every assignment and the rubric for evaluation is made completely transparent. They know their progress at all times.
]

```{r echo = FALSE}
countdown(minutes = 8, 
          bottom = 0, 
          font_size = "1em",
          warn_when = 10)
```

---

<center>
<iframe src="https://embed.polleverywhere.com/multiple_choice_polls/OMwwmmtRuyDcQfbdBG0Yb?controls=none&short_poll=true" width="800px" height="600px"></iframe>
</center>

---

<center>
<iframe src="https://embed.polleverywhere.com/multiple_choice_polls/8cPfH44JDibVtbX8CF66E?controls=none&short_poll=true" width="800px" height="600px"></iframe>
</center>

---