---
title: "Teaching Observations"
author: "STAT 375 UC Berkeley"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: solarized-light
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      fig.align = "center",
                      fig.retina = 3,
                      warning = FALSE)

library(tidyverse)
library(emo)
library(lorem)
library(xaringanthemer)
library(countdown)
source("https://raw.githubusercontent.com/andrewpbray/stat-375-website/master/xaringan-theme.R")
```

## While you're waiting

Please sit in pairs with someone who is teaching as similar a class to yours as possible.

---
## Agenda

1. Reflections from teaching
2. Observing a lesson
3. Guest: Elisa Stone, Director, CalTeach

---
class: middle, center, inverse

# Reflections from teaching

---
## Reflections from teaching

.task[
In your groups, take turns sharing:

1. One thing that went well
2. One thing that went poorly
3. One thing you learned
]

```{r echo = FALSE}
countdown(minutes = 10, bottom = 0)
```

---
class: middle, center

# Observing a Lesson

---
## Observing a Lesson

I will give a 20 minute lesson. You will have dual roles: **student** and **observer**.

### As an observer

- Please take _objective_ notes about what happens in during the lesson: what I do, what I say, and how students in the class respond.
- Refrain from making judgements.
- Periodically note the time at which various elements occur.


---
## Peer Observations

1. Meet your partner and decide on times when each of you will observe one anothers' class.

2. Share which element of teaching you'd each like your observer to focus on (e.g. timing, clear boardwork, students engagement)

3. Observe one another and take notes guided by the observation form.

4. Debrief your observations on 10/11 in class.

.task[
Please do 1-2 in pairs and enter your information in the google form:
[https://forms.gle/FWWNLFpnr6ciyE8B9](https://forms.gle/FWWNLFpnr6ciyE8B9)
]
